---
title: "app3"
author: Sun Young Park
output: html_document
---

```{r setup, include = FALSE}
library(latentnet)
library(coda); library(rgl)
library(mixedMem)
```

## 18 Monk (Sampson, 1986)

### characteristics
+ transitivity - distance model
+ one type of ties

```{r}
data(sampson)

# fitting models in a 2D space
samp.fit.2 <- ergmm(samplike ~ euclidean(d = 2))
samp.fit.2C <- ergmm(samplike ~ euclidean(d = 2, G = 3)) # with clustering (3 clusters)
samp.fit.2C4 <- ergmm(samplike ~ euclidean(d = 2, G = 4)) # with clustering (4 clusters)

# fitting model in a 3D space
samp.fit.3 <- ergmm(samplike ~ euclidean(d = 3))

# compare MCMC convergence diagnostics: Both mixing and stationarity are good.
mcmc.diagnostics(samp.fit.2)
mcmc.diagnostics(samp.fit.2C)
mcmc.diagnostics(samp.fit.2C4)
mcmc.diagnostics(samp.fit.3)
```


```{r }
# set colors
oneLF <- samplike %v% "group"
oneLF[c(1, 7, 15)] <- "Waverers"

oneLFcolors <- c("black", "blue", "red", "green")[match(oneLF, c("Turks", "Outcasts", "Loyal", "Waverers"))]

# plot the starting value
plot(samp.fit.2, what = "sampling.start") 

# plot the estimated latent positions
# [Note] MKL divergence: locations that minimize the divergence between the posterior distribution of distance created using the estimate of the location calculated from MLE, posterior mean, posterior mode
plot(samp.fit.2, label = oneLF, vertex.col = oneLFcolors,
	 labels = TRUE, vertex.cex = 3, print.formula = FALSE, plot.vars = FALSE,
	 main = "2D Z, without cluster")
plot(samp.fit.2C, label = oneLF,
	 labels = TRUE, pie = TRUE, vertex.cex = 3, print.formula = FALSE, cluster.col = c("green", "blue", "red"),
	 main = "3 clusters")
plot(samp.fit.2C4, label = oneLF,
	 labels = TRUE, pie = TRUE, vertex.cex = 3, print.formula = FALSE, cluster.col = c("blue", "red", "black", "green"),
	 main = "4 clusters")

# plot the posterior distirbutions
plot(samp.fit.2, what = "density") # why so blurry? Let's add colors
plot(samp.fit.2C, what = "density")
plot(samp.fit.2C4, what = "density")

# BIC
summary(samp.fit.2) 
summary(samp.fit.3) 
```

### MMSBM

```{r}
dim(as.matrix(samplike))
?mixedMemModel

Total <- 18
J <- 1
Rj <- rep(1, J)
Nijr <- array(1, dim = c(Total, J, max(Rj)))
K <- 3
Vj <- rep(1, J)
alpha <- rep(.2, K)
dist <- rep("bernoulli", J)
obs <- array(0, dim = c(Total, J, max(Vj), max(Nijr)))
obs[, 1, 1, 1] <- as.matrix(samplike)
```

## Tribes in New Guinea (Read, 1954)
A network of political alliances and enmities among the 16 Gahuku-Gama sub-tribes of Eastern Central Highlands of New Guinea

### characteristics
+ transitivity? - distance model
+ two types of tie

```{r}
data(tribes)

# only positive ties
tribes.fit <- ergmm(tribes ~ euclidean(d = 2, G = 3), response = "pos")

# plot
plot(tribes.fit, what = "sampling.start") 
plot(tribes.fit, pie = TRUE, main = " ") # color of edges

# three different types of ties
tribes.fit.b <- ergmm(tribes ~ euclidean(d = 2, G = 3), response = "sign.012",
					  family = "binomial.logit", fam.par = list(trials = 2))

# check the difference in models
plot(tribes.fit.b, what = "sampling.start") 
par(cex.main = 1.9, cex.lab = 1.2)
plot(tribes.fit.b,
	 edge.col = as.matrix(tribes, "pos", m = "a")*3 + as.matrix(tribes, "neg", m = "a")*2,
	 vertex.cex = 2.5, print.formula = FALSE,
	 pie = TRUE,
	 plot.vars = FALSE,
	 main = "Multiple Types of Ties") 
	# if we consider both ties, the network looks very different.

# diagnostics
mcmc.diagnostics(tribes.fit)
mcmc.diagnostics(tribes.fit.b)
```

## Stratification in Natchez, Mississippi (Davis, Gardner, and Gardner, 1941)
18 Southern women observed over a nine-month period in a series of 14 informal social events

### characteristics
+ allow the variance in individual activity - projection model
+ one type of ties

```{r}
data(davis)

# fit
davis.fit <- ergmm(davis ~ bilinear(d = 2, G = 2) + rsociality)

# plot
plot(davis.fit, what = "sampling.start") 
plot(davis.fit, pie = TRUE, rand.eff = "sociality", label = TRUE, vertex.cex = 1.5, print.formula = FALSE,
	 main = "Projection Model")
#
mcmc.diagnostics(davis.fit)
```

